\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-19 notes/2loopNLSM.tex
Fund BCJ + misc

Color-kinematics duality is a statement about the off-shell graphical simplicity that manifest redundancy in the on-shell observables of gauge and gravity theories. Ignoring factors of $i$ and the coupling constant, a generic $m$-point $L$-loop amplitude in a color-dual theory -- such as NLSM, YM, or bi-adjoint scalar theory -- can be written as
\be
\mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma n_\Gamma}{d_\Gamma} .
\ee
Here the spacetime dimension is $D$.
Even though the underlying theory may have quartic (or higher multiplicity) vertices, it is possible to multiply and divide by propagators so that the sum runs over only purely cubic graphs $\Gamma$.
Overcounting is removed by the internal symmetry factor $S_\Gamma$, which tracks the number of graph symmetries with external legs held fixed.
The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.  However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2023vjg, Carrasco:2020ywq} \jm{I cited DF$^2$, fundamental fermions, Aslan+JJ, Ingrid+JJ. Is there anything else anyone wants to mention?}.}
the denominator $d_\Gamma$ is the product of propagators associated with the graph $\Gamma$, and the numerator $n_\Gamma$ is all of the remaining kinematic factors including dot products of momenta and polarization vectors.

The color factors $c_\Gamma$ are not independent and are related to one another via a set of Jacobi identities that look schematically like
\be
c_i+c_j+c_k=0,
\ee
where $i$, $j$, and $k$ are three graphs.
Example Jacobi relations are presented in detail in \cref{sec:bootstrap}.
Color-kinematics duality states that there exists a way to rearrange factors between the various kinematic numerators $n_\Gamma$ such that the numerators obey all of the same Jacobi identities as the color factors
\be
n_i +n_j +n_k=0.
\ee
If color-kinematics duality can be achieved at the off-shell level, then the kinematic numerators should satisfy an algebra just like the color factors.
In theories where the kinematic algebra is known, it is often the algebra of volume preserving diffeomorphisms \cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz, Cheung:2021zvb, Cheung:2022mix}.
As a simple example, color-dual numerators for 4pt pion scattering at tree level are
\begin{align}
&n_s = s(t-u)\\
&n_t = t(u-s)\\
&n_u = u(s-t)
\end{align}
where the coupling has been normalized away.
These numerators sum to zero by explicit calculation.

@@

Many of the 1-loop results presented in \sect{} are informed by the tree-level double-copy so we will review the tree case here.
The color structure of tree-level amplitudes is particularly simple.
A fully color dressed tree amplitude $\mathcal{A}_n$ in YM, NLSM, or bi-adjoint scalar theory can be decomposed in terms of the trace basis
\be
\mathcal{A}_n = \sum \limits_{\sigma\in S_{n-1}} \text{Tr}(T^{a_{\sigma_1}} T^{a_{\sigma_2}}...T^{a_{\sigma_{n-1}}} T^{a_n}) A_n[\sigma_1, \sigma_2,...\sigma_{n-1}, n],
\ee
where $T^a$ are generators of the gauge group and, because of the cyclicity of the trace, one of the legs is held fixed so that the sum runs over the $(n-1)!$ permutations of the remaining external legs.
The coefficients of the color factors are the color-ordered partial amplitudes $A_n[...]$.
Any tree-level color factor can be converted into a linear combination of Del Duca-Dixon-Maltoni (DDM) half-ladder color factors
\be
\text{DDM}[a_1, a_2,... a_n] \equiv f^{a_1 a_2 b_1} f^{b_1 a_3 b_2} f^{b_2 a_4 b_3}...f^{b_{n-3} a_{n-1} a_n}
\ee
associated with the graph
\be
\halfLadder
\ee
by repeated application of the Jacobi identity \cite{DixonMaltoni}.
The fully color-dressed tree amplitude can then be re-expressed as
\be
\mathcal{A}_n = \sum \limits_{\sigma\in S_{n-2}} \text{DDM}[a_1, a_{\sigma_2}, a_{\sigma_3}, a_{\sigma_{n-1}}, a_n]  A_n[1, \sigma_2,...\sigma_{n-1}, n]
\ee
with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$ terms, indicating that there are additional relations (the Kleiss-Kuijf relations) amongst the partial amplitudes \cite{Kleiss:1988ne}.\footnote{The fundamental BCJ relations further reduce the basis of partial amplitudes down to $(n-3)!$ \cite{BCJ}.}
Since the Jacobi identity can be used to express any tree-level color factor in terms of the half ladders, it is enough to specify the numerators of the half ladder diagrams in order to satisfy color-kinematics duality at tree level.
At 1-loop, every diagram can be related to one topology as well, in this case the $n$-gon, but the pattern does not persist to 2-loops.

\subsection{Color-dual Lagrangians}
While BCJ relations is an on-shell statement about the color-dual nature of scattering amplitudes, one might aspire to hard code color-kinematics duality by realizing an off-shell Lagrangian description of the theory. The double-copy construction of \ref{DCconstruction} would suggest a manifestly cubic Lagrangian of the form:
\be
\mathcal{L} = P_V^{ab}P_W^{ij}\mathcal{O}^a_i \Box \mathcal{O}^b_j +  V^{abc} W^{ijk}\mathcal{O}^a_i \mathcal{O}^b_j \mathcal{O}^c_k
\ee
where $V^{abc}$ and $W^{ijk}$ are cubic Feynman rules mixing field operators $\mathcal{O}^{a}_i$ indexed by quantum numbers $a$ and $i$. We have introduced $P_V^{ab}$ and $P_W^{ij}$ projection operators to encode non-local kinetic structure that could in principle participate in the construction. Should the off-shell Feynman rules of this cubic theory be antisymmetric and satisfy Jacobi identities on all internal edges,
\begin{align}
\textit{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0\,,
\\
\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\,,
\end{align}
where 
\be
{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}V^{b_1a_3b_2}\cdots V^{b_{n-3} a_{n-2}a_n}\,.
\ee
This is a sufficient condition of the amplitudes to obey BCJ relations. Off-shell desciription of color-dual theories are rare, and only a few examples are available in the literature. Typically when one goes about construction color-dual theories directly from a set of cubic interactions, higher point Jacobi and antisymmetry constraints require introducing additional operators. See refs \cite{} for some recent examples. Indeed, as we'll show in \ref{cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point. Absent information about the kinematic algebra, one can make progress in the construction of loop-level color-dual amplitudes by employing a color-dual bootstrap. 
\subsection{Color-dual Bootstrap}
\label{sec:bootstrap}

@@

Color-kinematics duality is a statement about color factors, kinematic numerators, and the accompanying Jacobi relations.
Adjoint-type color factors are associated with cubic graphs, so satisfying color-kinematics duality implicitly requires expressing the integrand in terms of such graphs. As mentioned earlier, this is possible to do even for a theory with quartic (or higher multiplicity) vertices by multiplying and dividing by propagators.
In the case of the 4pt 2-loop example promised above, there are 14 cubic graph topologies (shown in Fig \sect{}) ignoring tadpoles and bubble on external leg (BEL) graphs.

@@

\section{One-loop cubic construction} \label{cubic}
Here we'll describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well. It has to do with how the vector state sum mixes with the four-point contact. Starting with the Yang-Mills Lagrangian,
\be
\mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2 + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
\ee
We can express the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
\be
T^k_{ij} = (\varepsilon_i\varepsilon_j)(\varepsilon_k p_i)
\ee
This kinematic generator is anti-symmetric in $1\leftrightarrow 2$ exchange, and from it we can construct the full Lorenz gauge Yang-Mills vertex by summing over cyclic permutations:
\be
V^{(123)}_{\text{YM}} = T^3_{12} +\text{cyc}(123)
\ee
Contracting this with the vector state sum, we can see that the cubic Yang-Mills vertex does not alone satisfy the four-point Jacobi identity:
\be\label{cubicJac}
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4+\text{cyc}(234) = \varepsilon_{(12)}  \varepsilon_{(34)} (s_{13}-s_{23}) +\text{cyc}(234) \neq 0
\ee
where $ \varepsilon_{(ij)} =  \varepsilon_{i}\cdot  \varepsilon_{j}$. Of course, it is not hard to see that one can simply absorb the remaining terms into the definition of the four-point kinematic numerators:
\be
{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4 = {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4 + s_{12} (\varepsilon_{(13)}\varepsilon_{(24)}-\varepsilon_{(14)}\varepsilon_{(23)})
\ee
where $V_{\text{YM}+B}$ indicates the introduction of an additional two-form studied in \cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian. 
\be
{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
\ee
where the new cubic Lagrangian is of the form:
\be
\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 - B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu A^c_\nu
\ee
Of course, higher multiplicity would require further redefinition of the three-point vertex to satisfy Jacobi identites on all internal edges. While introducing successively higher spin states could in principle work at tree level, we will see that it is not consistent with what we find at general loop order. We will comment on this in \sect{}. For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.

@@

Similar to the pion construction in \cref{sec:pions}, we use the
kinematic Jacobi relations to define the numerators for all cubic
graphs in terms of the two basis graphs, including allowing nontrivial
numerators on BEL diagrams.  We will simply avoid imposing constraints
that directly involve such pathological diagrams.  That leaves us with
14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc}, on
which to impose maximal cuts and symmetries.  Doing so, we are left
with AA total parameters in the unrestricted ansatz and BB total in
the BDN-restricted ansatz.
\begin{figure}
\centering
{\MCutC, \MCutD, \sumoCut, \MCutJ,  
 \\
  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
\\
\MCutI,  \MCutE, \MCutK, 
\\
 \MCutL, \MCutG,  \MCutH,
}
  \caption{The 14 non-pathological maximal-cut diagrams}
  \end{figure}

>>>>

Color-kinematics duality is a statement about the off-shell graphical simplicity that manifest redundancy in the on-shell observables of gauge and gravity theories. Ignoring factors of $i$ and the coupling constant, a generic $m$-point $L$-loop amplitude in a color-dual theory -- such as NLSM, YM, or bi-adjoint scalar theory -- can be written as
\be
\mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma n_\Gamma}{d_\Gamma} .
\ee
Here the spacetime dimension is $D$.
Even though the underlying theory may have quartic (or higher multiplicity) vertices, it is possible to multiply and divide by propagators so that the sum runs over only purely cubic graphs $\Gamma$.
Overcounting is removed by the internal symmetry factor $S_\Gamma$, which tracks the number of graph symmetries with external legs held fixed.
The color factor $c_\Gamma$ is the string of structure constants $f^{abc}$ associated with the graph $\Gamma$,\footnote{This paper is focused on theories with particles that transform in the adjoint.  However, the double copy can be applied to a far more diverse set of theories with particles that transform in the fundamental or more diverse representations, see for example \cite{Johansson:2017srf, Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2023vjg, Carrasco:2020ywq}.}
the denominator $d_\Gamma$ is the product of propagators associated with the graph $\Gamma$, and the numerator $n_\Gamma$ is all of the remaining kinematic factors including dot products of momenta and polarization vectors.

The color factors $c_\Gamma$ are not independent and are related to one another via a set of Jacobi identities that look schematically like
\be
c_i+c_j+c_k=0,
\ee
where $i$, $j$, and $k$ are three graphs.
Example Jacobi relations are presented in detail in \cref{sec:bootstrap}.
Color-kinematics duality states that there exists a way to rearrange factors between the various kinematic numerators $n_\Gamma$ such that the numerators obey all of the same Jacobi identities as the color factors
\be
n_i +n_j +n_k=0.
\ee
If color-kinematics duality can be achieved at the off-shell level, then the kinematic numerators should satisfy an algebra just like the color factors.
In theories where the kinematic algebra is known, it is often the algebra of volume preserving diffeomorphisms \cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz, Cheung:2021zvb, Cheung:2022mix}.
As a simple example, color-dual numerators for 4pt pion scattering at tree level are
\begin{align}
&n_s = s(t-u)\\
&n_t = t(u-s)\\
&n_u = u(s-t)
\end{align}
where the coupling has been normalized away.
These numerators sum to zero by explicit calculation.
Note that the $s$-channel numerator contains an explicit factor of $s$ that cancels with the propagator and the same goes for the $t$- and $u$-channels so that the net result is a local function, just as one would expect for the pion tree amplitude.

@@

Many of the 1-loop results presented in \cref{sec:cubic} are informed by the tree-level double-copy so we will review the tree case here.
The color structure of tree-level amplitudes is particularly simple.
A fully color dressed tree amplitude $\mathcal{A}_n$ in YM, NLSM, or bi-adjoint scalar theory can be decomposed in terms of the trace basis
\be
\mathcal{A}_n = \sum \limits_{\sigma\in S_{n-1}} \text{Tr}(T^{a_{\sigma_1}} T^{a_{\sigma_2}}...T^{a_{\sigma_{n-1}}} T^{a_n}) A_n[\sigma_1, \sigma_2,...\sigma_{n-1}, n],
\ee
where $T^a$ are generators of the gauge group and, because of the cyclicity of the trace, one of the legs is held fixed so that the sum runs over the $(n-1)!$ permutations of the remaining external legs.
The coefficients of the color factors are the color-ordered partial amplitudes $A_n[...]$.
Any tree-level color factor can be converted into a linear combination of Del Duca-Dixon-Maltoni (DDM) half-ladder color factors
\be
\text{DDM}[a_1, a_2,... a_n] \equiv f^{a_1 a_2 b_1} f^{b_1 a_3 b_2} f^{b_2 a_4 b_3}...f^{b_{n-3} a_{n-1} a_n}
\ee
associated with the graph
\be
\halfLadder
\ee
by repeated application of the Jacobi identity \cite{DixonMaltoni}.
The fully color-dressed tree amplitude can then be re-expressed as
\be
\mathcal{A}_n = \sum \limits_{\sigma\in S_{n-2}} \text{DDM}[a_1, a_{\sigma_2}, a_{\sigma_3}, a_{\sigma_{n-1}}, a_n]  A_n[1, \sigma_2,...\sigma_{n-1}, n]
\ee
with legs $1$ and $n$ fixed so that the sum only contains $(n-2)!$ terms, indicating that there are additional relations -- the Kleiss-Kuijf (KK) relations -- amongst the partial amplitudes \cite{Kleiss:1988ne}.
The KK relations are generic to any theory with purely adjoint particles.
Color-kinematics duality implies that the KK basis is overcomplete and can be reduced to a basis of $(n-3)!$ amplitudes via the fundamental BCJ identities \cite{BCJ}
\be
\sum \limits_{i=2}^{n-1} k_1 \cdot (k_2+...+k_i) A_n[2,...,i,1,i+1,...,n] =0.
\ee
In terms of constructing explicit color-dual solutions at tree level, it is enough to specify the numerator of the half ladder because any diagram can be reduced to a half ladder through successive applications of the Jacobi identity.
At 1-loop, every diagram can be related to one topology as well, in this case the $n$-gon, but the pattern does not persist to 2-loops.

\subsection{Color-dual Lagrangians}
While BCJ relations is an on-shell statement about the color-dual nature of scattering amplitudes, one might aspire to hard code color-kinematics duality by realizing an off-shell Lagrangian description of the theory. The double-copy construction of \ref{DCconstruction} would suggest a manifestly cubic Lagrangian of the form:
\be
\mathcal{L} = P_V^{ab}P_W^{ij}\mathcal{O}^a_i \Box \mathcal{O}^b_j +  V^{abc} W^{ijk}\mathcal{O}^a_i \mathcal{O}^b_j \mathcal{O}^c_k
\ee
where $V^{abc}$ and $W^{ijk}$ are cubic Feynman rules mixing field operators $\mathcal{O}^{a}_i$ indexed by quantum numbers $a$ and $i$. We have introduced $P_V^{ab}$ and $P_W^{ij}$ projection operators to encode non-local kinetic structure that could in principle participate in the construction. Should the off-shell Feynman rules of this cubic theory be antisymmetric and satisfy Jacobi identities on all internal edges,
\begin{align}
\textit{anti-symmetry}:& \quad{}_{a_1}\langle V^{a_2} \rangle_{a_3}+\text{cyc}(23)=0\,,
\\
\textit{Jacobi identity}:& \quad {}_{a_1}\langle V^{a_2} V^{a_3}\rangle_{a_4}+\text{cyc}(234)=0\,,
\end{align}
where 
\be
{}_{a_1}\langle V^{a_2}V^{a_3}\cdots V^{a_{n-1}} \rangle_{a_n} \equiv V^{a_1a_2b_1}V^{b_1a_3b_2}\cdots V^{b_{n-3} a_{n-2}a_n}\,.
\ee
This is a sufficient condition of the amplitudes to obey BCJ relations. Off-shell desciription of color-dual theories are rare, and only a few examples are available in the literature. Typically when one goes about construction color-dual theories directly from a set of cubic interactions, higher point Jacobi and antisymmetry constraints require introducing additional operators. See refs \cite{} for some recent examples. Indeed, as we'll show in \cref{sec:cubic}, Yang-Mills requires introducing a cubic 2-form interaction in order to manifest the kinematic algebra just at four-point. Absent information about the kinematic algebra, one can make progress in the construction of loop-level color-dual amplitudes by employing a color-dual bootstrap. 
\subsection{Color-dual Bootstrap}
\label{sec:bootstrap}

@@

Color-kinematics duality is a statement about color factors, kinematic numerators, and the accompanying Jacobi relations.
Adjoint-type color factors are associated with cubic graphs, so satisfying color-kinematics duality implicitly requires expressing the integrand in terms of such graphs. As mentioned earlier, this is possible to do even for a theory with quartic (or higher multiplicity) vertices by multiplying and dividing by propagators.
In the case of the 4pt 2-loop example promised above, there are 14 cubic graph topologies (shown in \cref{fig:MaxCuts}) ignoring tadpoles and bubble on external leg (BEL) graphs.

@@

\section{One-loop cubic construction}
\label{sec:cubic}
Here we'll describe why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well. It has to do with how the vector state sum mixes with the four-point contact. Starting with the Yang-Mills Lagrangian,
\be
\mathcal{L}^{\text{YM}} = -\frac{1}{2}(\partial_\mu A_\nu)^2 + f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu + f^{abe}f^{ecd}A^a_\mu A^b_\nu  A^c_\mu A^d_\nu 
\ee
We can express the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
\be
T^k_{ij} = (\varepsilon_i\varepsilon_j)(\varepsilon_k p_i)
\ee
This kinematic generator is anti-symmetric in $1\leftrightarrow 2$ exchange, and from it we can construct the full Lorenz gauge Yang-Mills vertex by summing over cyclic permutations:
\be
V^{(123)}_{\text{YM}} = T^3_{12} +\text{cyc}(123)
\ee
Contracting this with the vector state sum, we can see that the cubic Yang-Mills vertex does not alone satisfy the four-point Jacobi identity:
\be\label{cubicJac}
{}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4+\text{cyc}(234) = \varepsilon_{(12)}  \varepsilon_{(34)} (s_{13}-s_{23}) +\text{cyc}(234) \neq 0
\ee
where $ \varepsilon_{(ij)} =  \varepsilon_{i}\cdot  \varepsilon_{j}$. Of course, it is not hard to see that one can simply absorb the remaining terms into the definition of the four-point kinematic numerators:
\be
{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4 = {}_1\langle V^{2}_{\text{YM}}V^{3}_{\text{YM}}\rangle_4 + s_{12} (\varepsilon_{(13)}\varepsilon_{(24)}-\varepsilon_{(14)}\varepsilon_{(23)})
\ee
where $V_{\text{YM}+B}$ indicates the introduction of an additional two-form studied in \cite{Ben-Shahar:2022ixa} for constructing the NMHV Yang-Mills Lagrangian. 
\be
{}_1\langle V^{2}_{\text{YM}+B}V^{3}_{\text{YM}+B}\rangle_4+\text{cyc}(234) =0
\ee
where the new cubic Lagrangian is of the form:
\be
\mathcal{L}^{\text{YM}+B} = -\frac{1}{2}(\partial_\mu A_\nu)^2 - B_{\mu\nu}\Box\tilde{B}_{\mu\nu}+ f^{abc} \partial_\mu A^a_\nu A^b_\mu A^c_\nu+ f^{abc} (B_{\mu\nu}+\Box \tilde{B}_{\mu\nu})^a A^b_\mu A^c_\nu
\ee
Of course, higher multiplicity would require further redefinition of the three-point vertex to satisfy Jacobi identites on all internal edges. While introducing successively higher spin states could in principle work at tree level, we will see that it is not consistent with what we find at general loop order. We will comment on this in \sect{}. For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above.

@@

Similar to the pion construction in \cref{sec:pions}, we use the
kinematic Jacobi relations to define the numerators for all cubic
graphs in terms of the two basis graphs, including allowing nontrivial
numerators on BEL diagrams.  We will simply avoid imposing constraints
that directly involve such pathological diagrams.  That leaves us with
14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc}, on
which to impose maximal cuts and symmetries.  Doing so, we are left
with AA total parameters in the unrestricted ansatz and BB total in
the BDN-restricted ansatz.
\begin{figure}
\centering
{\MCutC, \MCutD, \sumoCut, \MCutJ,  
 \\
  \doubleBoxCut,  \crossBoxCut,\pentaTriangleCut,  \MCutF, 
\\
\MCutI,  \MCutE, \MCutK, 
\\
 \MCutL, \MCutG,  \MCutH,
}
  \caption{The 14 non-pathological maximal-cut diagrams} \label{fig:MaxCuts}
  \end{figure}
